---
title: "FML_Assignment3"
author: "Sandhya Cheepurupalli"
date: "2022-10-16"
output:
  pdf_document: default
  html_document: default
---
## Following Packages are required to run the following code
```{r Packages}
library(caret)
library(dplyr)
library(ISLR)
library(e1071)
```

# Step-1 Reading the dataset
```{r Reading dataset}
setwd("C:\\Users\\sandh\\Downloads")
mydata<-read.csv(file='UniversalBank.csv')
mydata$Personal.Loan<-as.factor(mydata$Personal.Loan)
mydata$Online<-as.factor(mydata$Online)#converting to factor
mydata$CreditCard<-as.factor(mydata$CreditCard)#converting to factor

```
## Step-2 Removing unwanted data from the dataset
```{r Cleansing data}
mydata1<- mydata %>% select(Personal.Loan, Online, CreditCard)
head(mydata1)
```

## Step-3 Partitioning dataset into training data and validation data
```{r}
set.seed(7)
Train_Index = createDataPartition(mydata1$Personal.Loan,p=0.60, list=FALSE) 
# 60% of remaining data as validation
Train_Data = mydata1[Train_Index,]
Validation_Data = mydata1[-Train_Index,]
head(Train_Data)
```
## Question-A Creating Pivot Table with Online as Column and CC & Loan as rows
```{r pivot1}
table1<- ftable(Train_Data$Online,Train_Data$Personal.Loan,Train_Data$CreditCard, 
                row.vars = c(2,3),dnn=c('Online','Personal.loan','CreditCard'))
table1
```
## Question-B Finding the Probability for P(Loan=1 | P(CC=1), P(Online=1)) from the above Pivot Table
```{r}
P.loan<-table1[4,2]/(table1[2,2]+table1[4,2])
P.loan
```
## Question-C Creating two Pivot Tables - One for Loan as Rows and Online as Columns - Other for Loan as Rows and CC as Columns
```{r pivot2 and 3}
table2<- ftable(Train_Data$Online,Train_Data$Personal.Loan,row.vars = c(2), 
                dnn=c('Online','Personal.loan'))
table2
table3<- ftable(Train_Data$CreditCard,Train_Data$Personal.Loan,row.vars = c(2), 
                dnn=c('CreditCard','Personal.loan'))
table3
```
## Question-D Finding Probabilities for P(CC=1 | Loan =1), P (Online=1 | Loan=1), P(Loan=1), P(CC=1 | Loan = 0), P(Online=1 | Loan=0), P(Loan=0)
```{r question D}
p.CC1.loan1<-table3[2,2]/(table3[2,1]+table3[2,2])
p.CC1.loan1
p.online1.loan1<-table2[2,2]/(table2[2,1]+table2[2,2])
p.online1.loan1
p.CC1.loan0<-table3[1,2]/(table3[1,1]+table3[1,2])
p.CC1.loan0
p.online1.loan0<-table2[1,2]/(table2[1,1]+table2[1,2])
p.online1.loan0
p.loan1<-filter(Train_Data, Personal.Loan==1) %>% count()
p.loan1<-p.loan1[[1]]/3000
p.loan1
p.loan0<-filter(Train_Data, Personal.Loan==0) %>% count()
p.loan0<-p.loan0[[1]]/3000
p.loan0
```
## Question-E Finding Naive Bayes Probability for P(Loan=1 | CC=1, Online=1) using the Above Probabilities
```{r Question E Naive Bayes}
Naive.Bayes<-(p.CC1.loan1*p.online1.loan1*p.loan1)/((p.CC1.loan1*p.online1.loan1*p.loan1)+
                                                      (p.CC1.loan0*p.online1.loan0*p.loan0))
Naive.Bayes
```
## Question-F Comparing value obtained from Question-B and Question-E
$$\text{The probability of P(Loan=1 | CC=1, Online=1) from Question-B is 0.09814815 while from Question-E is 0.1016095.}$$

$$\text{It is clearly seen that the probability of Question-E > Question-B.}$$
$$\text{This difference is because, we have considered CC and Online as conditionally independent variables in Question-E.}$$ 
$$\text{The probability of B is more accurate as we have not considered CC  and Online as conditionally independent variables.}$$

## Question-G Finding Probability of P(Loan=1 | CC=1, Online=1) using Naive Bayes Function
```{r Question G}
Question.G<-naiveBayes(Personal.Loan ~ ., data = Train_Data)
Question.G
Ans<-predict(Question.G,Validation_Data, type="raw")
head(Ans)
```
$$\text{It is found that the conditional probabilities from Question-D and Question G are equal.}$$
$$\text{Which can be interpreted as Naive Bayes probabilities from Question E and G will also be equal.}$$