---
title: "Assignment1_Sep11"
author: "Sandhya Cheepurupalli"
date: "2022-09-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages

Below are the packages that were installed

```{r eval=TRUE}
require(tidyverse)
require(car)
library(tidyverse)
library(car)

```
### Importing DataSet
In this section a data set from a .csv file is imported into RStudio and the data is printed

```{r Importing DataSet}
salesdata <- read.csv("https://query.data.world/s/wtwashv6h4f4ykobpecvrfo3ejwqts", header=TRUE, stringsAsFactors=FALSE);
print(salesdata)
```
### Descriptive Statistics
Here we summarize each of the columns in the dataset
```{r Descriptive}
summary(salesdata)
```
### Transforming Variable in the Dataset
In this section we have created a new dataset from the previous one. The new dataset has a lesser number of columns from the previous. After creating a new dataset we renamed the columns in the dataset.

```{r Descriptive Statistics}
new_salesdata <- salesdata %>% select(Country, Item.Type, Sales.Channel, Units.Sold, Unit.Price, Unit.Cost, Total.Revenue, Total.Profit)
names(new_salesdata) <- c('Country_Name', 'Item_Type', 'Sales_Channel_Type', 'Units_Sold', 'Unit_Price', 'Unit_Cost', 'Total_Revenue', 'Total_Profit')
```

### Including Plots 


```{r Plots}
Sales_channel <- table(new_salesdata$Sales_Channel_Type)
labs <- paste(names(Sales_channel), "\n", Sales_channel, sep="")
pct <- (Sales_channel/sum(Sales_channel)*100)
labs <- paste(labs, pct) # add percents to labels
labs <- paste(labs,"%",sep="") # ad % to labels
pie(Sales_channel,labels = labs, col=rainbow(length(labs)),
    main=" Pie chart of Sales channel type")

scatterplot(Total_Profit ~ Total_Revenue| Sales_Channel_Type, data = new_salesdata)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
